Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-12 paper/main.tex
revise Intro and Method

\todo[inline]{doing the
    revision of the result section I realized that we probably should
    ``somehow'' add that clusters should not be all over the place but spatially
    constrained to the parahippocampal and neighbouring cortices, because
    naturalistic stimulus / possibly confounding variables}

@@

\begin{itemize}
\item Struktur des letzten Absatzes finde ich
    bisher nicht so geil (Hypothesen kommen recht spät (d.h. nach Methode),
    Results folgen direkt darauf
\end{itemize}

\noindent Method (after stimulus description):

\begin{itemize}
\item key strategy to address this question
\item auch VIS hat mehrere Kontraste
\item neuer Abschnitt 2.6: all regressoren und Kontraste; Kontraste sind abiträr
    aber ist ok; 2.7: eigentliche Statistische Analyse
\item which specific cognitive processing do we contrast in AD vs. AV?
\item ``ingredients'' to make it happen? we have some annotations at hand;
    define congruent contrasts based on regressors that are built from
    annotations; available annotations could be described in a dedicated
    section (COH: should be shorty and very high-level; details probably will
    confuse the shit out of readers)
\item what do we need to check to ensure subsequent analyses are valid (COH:
    this is the part that is the most elusive to me when it comes to precise
    phrasing)? a) correlation of regressors, b) negative controls
\end{itemize}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.
\todo{phrasing might be strange but aims to delineate
from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
but imo that does not say anything about excitation/inhibition}
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed by
contrasting selected stimulus features that incidentially occur under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
Based on these annotations, we created several general linear model (GLM)
contrast to analyze the corresponding publicly available fMRI datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.
% varying amount of data
Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{rewrite if it should be
mentioned}

% hypo a
We hypothesize[d] that whole-brain analyses will/would reveal increased
hemodynamic activity in the PPA as functionally defined by a visual localizer
experiment using static pictures done with the same subjects
\citep{sengupta2016extension}.
% hypo b
Focussing on the [``cleaner operationalization'' of the] audio-description, we
further hypothesize[d] that an exclusively auditory stimulus can/could
substitute a block-design experiment using pictures to localize a ``visual
area'' in individual subjects.
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions as a block-designed
visual localizer experiment.\todo{interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lasty, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

\todo[inline]{the topic anteriorer vs. posterior is mentioned first at the very
and of the intro and occurrs as "surprising" in the intro as in our results
(it's mentioned in the abstract though)}

@@

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) ) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}
(displayed at a size of approximately
\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle).
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

% AD
In the AD study, visual instructions were presented on a rear-projection screen
inside scanner bore. During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue.
% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen
% screen size
at a viewing distance of \unit[63]{cm}, with a movie frame projection size of
\unit[23.75 $\times$ 10.25]{cm}.\todo{replace with visual angle size, in line with VIS}
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.

% AD & AV: auditory stimulation
Auditory stimulation was implemented using custom in-ear (AD), or over-the-ear
headphones (AV), which reduced the scanner noise by
at least \unit[20–30]{dB}.

@@

\subsubsection{Stimulus annotation and regressors}

@@

% intro
Since we did not design the naturalistic stimuli for detection power, we
annotated the temporal structure of the fixed stimuls material to operationalize
the perception of different stimulus features and create regressors for the
following GLM analysis.

\paragraph{audio-description: annotation}

% AD annotation
For the analysis of the AD stumulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% reference to table with rules and examples
A complete overview of all 18 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in
a] disco'', ``[the platoon wades through a] rice field''). They also comprise
words that could count as a member of another categories in case the narrator
uses these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').

@@

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
% rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment depicted in the movie.

@@

% AV events
For the analysis of the AV stimulus, we used a previously published annotation
[of the 869] movie cuts and depicted locations \citep{haeusler2016cutanno} to
created regressors based on the kind of location that is depicted in the movie
frame after a cut.

@@

% AV regressors/events
Each location was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

% irrespectible of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables (e.g. presence of
faces).
% AV COPEs: intro
The rationale that this approach would still yield categories correlating with
increased hemodynamic activity in the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal, grill2006repetition}.
% null regressor
As for the regressors for AD stimulus, a null regressor was chosen for a
regressor in a segment if that segment did not contain an event of the
corresponding category.
% no cut condition: intro
A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
created as a control condition to create negative control contrasts:
% procedure
Frames were drawn from movie shots lasting at least \unit[20]{s} and had to have
a minimum distance of \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

% reference to figure ``correlation of regressors''
We computed the Pearson coefficients of the regressors across the eight segments
of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
Figure \ref{fig:reg-corr}) which suggest the models should not suffer from low
detection power due to shared variance among regressors.
%
\todo[inline]{discussion of the regressors correlation at the very beginning of
discussion could be pasted here; will save space there but will mix methods/
results/ discussion here}

@@

\todo[inline]{SE: Das mit den 8 kontrasten und 5 kontrasten habe ich nicht
intuitiv durchblickt. Was wurde da gegen was kontrastiert? COH: revised but
maybe still not optimal}

% intro
To test the robustness our approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in event counts.
% thus: primary contrasts
We chose one ``primary contrast'' for every stimulus before running the
analyses.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.\todo{oh, lord!}

@@

@@

\begin{itemize}
\item RSC (and ventral precuneus): 7 contrasts (all bilateral)
\item lateral occipiatal cortex: 6 contrasts (4 bilateral, 2 unilateral =
    transverse occipital sulcus / occipiatal place area?; AD \& AV clusters
    overlap but AD clusters are more lateral, AV cluster are more medial \&
    caudal)
\item right superior temporal gyrus (auditory cortices): 4 contrasts
\item (smallish) prefrontal clusters: 3 contrasts (non-overlapping)
\end{itemize}

@@

\paragraph{AV: other signficant clusters across contrasts}

@@

% AV stimulus
AV stimulus. All contrasts using ``no cut condition'' > XY yield null results.
The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
parietal lobe. Compate Figure \ref{fig:reg-corr}: nouns that cue change to a new
setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
second highest correlation of a verbal cue category with a cut category; AND:
nouns that cue change to a familiar setting are somewhat correlated with cuts to
a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
category with a cut category).

@@

\subsection{correlation of regressors}

\todo[inline]{Following paragraph could pasted into method section to save space
here; a short interpretation is given there already; so methods/ results/
discussion are not absolutely separated there already}
% stimuli not designed for research purposes
The audio-description and the movie were not designed to be used in a BOLD fMRI
experiment but to entertain their audiences.
%
As a results, stimulus features that we annotated to create the regressors could
have been correlated leading to shared variance that lowers detection power.
% computing the correlations
Hence, we first tested for correlation of regressors within and across both
naturalistic stimuli (s. Figure \ref{fig:reg-corr})
% results of computing feature correlation
Results reveal no to minor correlations of regressors with regressors of the
same stimulus.
% encouraged by that we build contrasts (statement)
Thus, we felt encouraged to create traditional/canonical voxel-wise GLMs that
modeled and contrasted hemodynamic activity similarly to previous studies that
used conceptualized stimuli.

@@

% but
Nevertheless, results are still influcended by [sensitive to] the amount of
available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AD stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

@@

\todo[inline]{AV: field size decreases later in the movie; this is a confound
based on cinematography => the stimulus changes over time}

>>>>

@@

\begin{itemize}
    \item structure of last paragraph might be meh: methods/our approach
-> hypotheses -> results; readers might assume HARKing?
\end{itemize}

\noindent Method:

\begin{itemize}

\item at the moment "Annotation, Regressors and Contrasts" follows
    "Preprocessing" (right before "Statistical Analysis" as we agreed on); going
        back and forth a couple of times, imo there is no perfect location (at
        least in case we do not split that part into "Annotation" and
        "Regressors \& Contrasts" again.

\item structure of ``Annotation, Regressors \& Contrasts'' !! -> everything has
    pros and cons (at the moment lots of subheading since easier to navigate);
    at the moment I think (again) it makes more sense to mention AD first since
    it is the focus of the movie and the AV serves as, well, what exactly?

\item what do we need to check to ensure subsequent analyses are valid;
    a) correlation of regressors (first "sanity check" but more a prerequisite)
    b) negative controls (actual sanity check)

\end{itemize}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.\todo{phrasing to delineate from Huth
(2016); imo voxel-wise semantic modeling says nothing about
excitation/inhibition}
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed by
contrasting selected stimulus features that incidentally occur under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
Based on these annotations, we created several general linear model (GLM)
contrast to analyze the corresponding publicly available fMRI datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.
% varying amount of data
Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{rewrite if it should be
mentioned}

% hypo a
We hypothesize[d] that whole-brain analyses will/would reveal increased
hemodynamic activity spatially constrained \todo{i.e. not activity all over the
place} to the PPA as functionally defined by a visual localizer experiment using
pictures done with the same subjects.  \citep{sengupta2016extension}.
% hypo b
Focussing on the [``cleaner operationalization'' of the] audio-description, we
further hypothesize[d] that an exclusively auditory stimulus can/could
substitute a block-design experiment using pictures to localize a ``visual
area'' in individual subjects.
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions the block-designed
visual localizer.\todo{interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lastly, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

\todo[inline]{the topic anterior vs. posterior is mentioned at the end of the
intro for the first time; might be "surprising" but that is in line how the
story went (it's mentioned in the abstract though)}

@@

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}.\todo{I guess they only report the ones they
designed themselves in detail? -> check again}
%
There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}
(displayed at a size of approximately
\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle).
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

% AD
In the AD study, visual instructions were presented on a rear-projection screen
inside scanner bore. During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue.
% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen
% screen size \unit[23.75 $\times$ 10.25]{cm}
at a viewing distance of \unit[63]{cm}, with a movie frame projection size
approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
% AD & AV: auditory stimulation
Auditory stimulation was implemented using custom in-ear (AD), or over-the-ear
headphones (AV), which reduced the scanner noise by
at least \unit[20–30]{dB}.

@@

\subsection{Annotation, regressors, contrasts}

@@

\todo[inline]{key strategy to address research question -> operationalize
    perception of spatial information in naturalistic stimuli that are
ecologically more valid}

% traditionally
Traditionally, researchers specifically design stimuli that presumably would
trigger the perceptual process of interest while also controlling confounding
variables (e.g. color, luminance).
% our approach: annotation and regressors
Naturalistic stimuli [might] more closely mimic how we experience the world
around us but have the drawback that they are usually fix and that their
temporal structure of embedded stimulus features is unknown.\todo{phrasing}
% annotation ftw
Hence, we annotated a variety of stimulus features that later served as a basis
for GLM regressors.
% contrasts
Based on these regressors, we then created $t$-contrasts that we presumed to
subtract variance correlating with the perception of non-spatial information
from variance correlating with the perception of spatial information.

\subsubsection{Annotations \& regressors}

\paragraph{Audio-description: annotation}

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% reference to table with rules and examples
A complete overview of all 18 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in
a] disco'', ``[the platoon wades through a] rice field''). They also comprise
words that could count as a member of another categories in case the narrator
uses these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').

@@

% AV anno
For the analysis of the AV stimulus, we took advantage of a previously published
annotation of [the 869] movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.

@@

% rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either by changing the perspective
within a setting or switching to another setting.

@@

% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale (e.g. room) that
was depicted for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables (e.g. presence of
faces).
% AV COPEs: intro
The rationale that this approach would still yield categories correlating with
increased hemodynamic activity in the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points
\citep{epstein1999parahippocampal, grill2006repetition}.
% null regressor
As for the regressors for AD stimulus, a null regressor was chosen for a
regressor in a segment if that segment did not contain an event of the
corresponding category.
% no cut condition: intro
A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
created as a control condition to create negative control contrasts:
% procedure
Frames were drawn from movie shots lasting at least \unit[20]{s} and had to have
a minimum distance of \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

% stimuli not designed for research purposes
The audio-description and the movie were not designed to be used in a BOLD fMRI
experiment but to entertain their audiences.
% fixed time course; detection power
Since we annotated events in fixed time courses that could not experimentally
manipulated, regressors that are based on these events could be correlated
leading to shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we first tested for correlation of regressors across the eight segments
of each stimulus and correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of regressors of the same stimulus [which suggest the models should
not suffer from low detection power due to shared variance among regressors].
% correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli. This was expected and served as ``sanity check'' since the
audio-track of the audio-description is the audio-track of the movie but
featuring the additional narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ingredients" to answer our questions (cf. intro); we have annotations; define
% congruent contrasts based on regressors based on annotations

% repeat key question (cf. end of intro)
The key question of the current study was if a) we could operationalize the
perceptual processes in an audio-visual and exclusively auditory
naturalistic stimulus and if b) contrasting that fcompared to an
operationalization of non-spatial perception  would yield to increased
hemodynamic activity in the PPA as defined by a visual localizer experiment.
% difference (kinda repetition)
Instead of carefully selecting and designing conceptualized/simplified stimuli
that we assumed to match the proposed perceptual processes, we selected and
categorized stimulus features (movie cuts and spoken nouns) that are embedded in
two naturalistic stimuli.
% intro
To test the robustness of our approach, we operationalized the
perception of spatial information compared to the perception of ``non-spatial''
information differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).\todo{make ref to what is no "Audio-description: annotation"}
% thus: primary contrasts
For each stimulus, we chose one contrast to be ``primary contrast'' for further
inspection and a detailed report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.

@@

\todo[inline]{one could write more about the different contrast in Segupta et
al. here, but imo it's sufficient to point that out in the results given that
all subjects except two used the strict set given contrasts of VIS study and
that the ``best working'' will be used}

\todo[inline]{Nevertheless, state it in one sentence and check Berman, M. G. et al. Evaluating functional localizers: The case of the FFA. NeuroImage 50, 56–71 (2010)}

Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
alternative contrasts (strict, relaxed, or simple contrast), future studies that
aim for individual diagnostics / ROI localization should also test more than one
contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
shitty}

@@

\begin{itemize}
\item RSC (and ventral precuneus): 7 contrasts (all bilateral)
\item lateral occipital cortex: 6 contrasts (4 bilateral, 2 unilateral =
    transverse occipital sulcus / occipiatal place area?; AD \& AV clusters
    overlap but AD clusters are more lateral, AV cluster are more medial \&
    caudal)
\item right superior temporal gyrus (auditory cortices): 4 contrasts
\item (smallish) prefrontal clusters: 3 contrasts (non-overlapping)
\end{itemize}

@@

\paragraph{AV: other significant clusters across contrasts}

@@

% AV stimulus
AV stimulus. All contrasts using ``no cut condition'' > XY yield null results.
The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
parietal lobe. Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new
setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
second highest correlation of a verbal cue category with a cut category; AND:
nouns that cue change to a familiar setting are somewhat correlated with cuts to
a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
category with a cut category).

@@

@@

% but
Nevertheless, results are still influenced by [sensitive to] the amount of
available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AD stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

@@

\todo[inline]{AV: field size decreases later in the movie; this is a confound
based on cinematography => the stimulus changes over time; AV analysis exploits
confound structure}
